GNSS displacement detection based on Bayesian inference

### 2020-11-15 paper/manuscript.tex
add random walk try

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method. Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields. Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence. Displacement detection involves automatic identification of the time of displacement and determination of displacement. GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results.

%位移探测算法回顾，传统位移探测的弊端
%位移探测的短板
%本文拟采取的措施弥补这些短板
%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
%引入本文的研究内容和贡献
%引入文章结构

@@

\begin{equation}\label{eq_bayesian_prior_tau_5}
P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}
Through \ref{eq_bayesian_prior_tau_basic} and \ref{eq_bayesian_prior_tau_5}, the joint probability of all change points can be determined. Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.

@@

\end{figure*}
By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
\begin{equation}
\label{eq_rtk_measure}
{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
\end{equation}
where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $. After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. To obtain high precision positioning results, it is necessary to fix the integer ambiguity. The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
\begin{figure*}
	\begin{equation}
	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
	\label{eq_lamda}
	\end{equation}
\end{figure*}
There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one. The integer ambiguity is obtained by the integer least square method. Then, the test process is executed to determine whether to accept or reject the integer ambiguity\citep{wang2014ambiguity,wang2018improving}. If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.

@@

\section{Experiments and Results}
To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation experiments and field experiments. In the simulation experiment, the data affected by different noises are simulated. In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
\subsection{Simulation experiment}

@@

%
\section*{Conflict of Interest}
The authors declare that they have no conflict of interest.
\section*{Author Contributions}
Conceptualization: Nan Shen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
 \section*{Data Availability}

>>>>

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields. 
Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
Previous studies on displacement detection based on GNSS pay more attention to how to improve the positioning accuracy. The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.
%位移探测算法回顾，传统位移探测的弊端
%位移探测的短板

%本文拟采取的措施弥补这些短板
%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情

%引入本文的研究内容和贡献

%引入文章结构

@@

\begin{equation}\label{eq_bayesian_prior_tau_5}
P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}
Through \ref{eq_bayesian_prior_tau_basic} and \ref{eq_bayesian_prior_tau_5}, the joint probability of all change points can be determined. Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.
\begin{figure}[H]
	\centering
	\includegraphics[width=8 cm]{v_simple_p_model}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_simple_p_model}
\end{figure}

@@

\end{figure*}
By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
\begin{equation}
\label{eq_rtk_measure}
{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
\end{equation}
where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $. After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. To obtain high precision positioning results, it is necessary to fix the integer ambiguity. The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
\begin{figure*}
	\begin{equation}
	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
	\label{eq_lamda}
	\end{equation}
\end{figure*}
There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one. The integer ambiguity is obtained by the integer least square method. Then, the test process is executed to determine whether to accept or reject the integer ambiguity. If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.

@@

\section{Experiments and Results}
To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation experiments and field experiments. In the simulation experiment, the data affected by different noises are simulated. In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
\subsection{Simulation experiment}
\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_sim_simple_gauss_ts}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_sim_simple_gauss_ts}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_tau_sim_simple}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_tau_sim_simple}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_sigma_sim_simple}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_sigma_sim_simple}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_mu_sim_simple}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_mu_sim_simple}
\end{figure}

@@

%
\section*{Conflict of Interest}
The authors declare that they have no conflict of interest.
\section*{Author Contributions}
Conceptualization: Nan Shen, Liang Chen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
 \section*{Data Availability}
